%to do:
% check ILP book info
% web site

\documentstyle[11pt]{article}

\setlength{\textheight}{9.25in}
\setlength{\textwidth}{7in}
\setlength{\oddsidemargin}{-0.5in}
\setlength{\evensidemargin}{-0.5in}
\setlength{\topmargin}{-0.5in}
\renewcommand{\topfraction}{0.99}
\renewcommand{\bottomfraction}{0.99}
\renewcommand{\textfraction}{0.01}

\newcommand{\prt}[1]{\vspace{\baselineskip}

{\noindent \bf #1:}}
\newcommand{\prti}[2]{\vspace{\baselineskip}

\noindent {\bf #1.} #2}
\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}
\newcommand{\bd}{\begin{description}}
\newcommand{\ed}{\end{description}}

\begin{document}

\begin{center}
{\bf William W. Cohen}\\
%6941 Rosewood St, Pittsburgh, PA 15208\\
Center for Automated Learning and Discovery\\
Carnegie Mellon University\\
5000 Forbes Ave, Pittsburgh, PA 15213 \\
Email: {\tt william@wcohen.com}\\
Web: {\tt http://www.wcohen.com}\\
\end{center}

\prt{Professional Experience}
\bi
\item May 2003--present. {\it Associate Research Professor, Center for 
Automated Learning and Discovery, Carnegie-Mellon University,
Pittsburgh, PA}. 
\item July 2002--May 2003. {\it Visiting Associate Professor, Center for 
Automated Learning and Discovery, Carnegie-Mellon University,
Pittsburgh, PA}.  Conducted joint research with Steve Fienberg
(Statistics), John Lafferty (Computer Science), Tom Mitchell (CALD),
and Robert Murphy (Biology).
\item April 2000--May, 2002. {\it Distinguished Research Scientist,
Whizbang Labs, Pittsburgh, PA}. Conducted and supervised research and
development for an information extraction company.
\item November 2000--present. {\it Adjunct Faculty, Center for Automated
Learning and Discovery, Carnegie Mellon School of Computer Science.}
\item July 1999---April 2000. {\it Technology Consultant, AT\&T
Labs-Research, Shannon Laboratories, Florham Park NJ}. Senior research
scientist in the Machine Learning and Information Retrieval Research
Department. 
\item February 1996---July 1999. {\it Principle Research Staff Member,
AT\&T Labs-Research, Shannon Laboratories, Florham Park NJ}. Research
scientist in the Machine Learning and Information Retrieval Research
Department.
\item September 1990---February 1996. {\it Member Technical Staff, AT\&T Bell
Laboratories, Murray Hill NJ}. Research scientist in the Artificial
Intelligence Research Department and (later) in the
Information Extraction Research Department.
\item September 1994---October 1994. {\it Visiting Senior Research Associate,
Basser Department of Computer Science, University of Sydney, Sydney,
Australia.}  Conducted research in the research group
headed by Dr.~J.~R.~Quinlan.
\item Summer 1988. {\it Summer Intern, Bell Communications
Research, Piscataway NJ}.  Integration of natural-language front end
to an advanced planning system.
\item Summer 1987. {\it Research Assistant, Rutgers University
Computer Science Department, New Brunswick, NJ}. Extension of the
learning subsystem of a knowledge-based expert system for VLSI circuit
design.
\item November 1985---August 1986. {\it Member Technical Staff,
Computer Science Corporation, under contract to the Space Telescope
Science Institute, Baltimore MD.} Design and implementation of a
natural language query system as part of a decision support system for
selecting observations to be run on the Hubble Space Telescope.
\item June 1984---September 1985. {\it Computer Aided Design R\&D Specialist, 
General Electric Microelectronics Center, Research Triangle Park, NC.}
Project leader for an expert system project on optimization of
combinational logic.
\ei

\newpage

\prt{Education}

\prti{Ph.D. in Computer Science}{Rutgers University, New Brunswick, New
Jersey.  August 1990. 4.0/4.0 average.  Doctoral thesis, {\it
Explanation Based Generalization as an Abstraction Mechanism for
Concept Learning}, under the direction of Dr. Alex Borgida.}
AT\&T Bell Laboratories Fellowship, September 1989---August 1990;
Marion Johnson Fellowship, September 1986---June 1989.

\prti{M.S. in Computer Science}{Rutgers University, New Brunswick, New
Jersey. May 1988.  4.0/4.0 average.}

\prti{B.S. in Computer Science}{Duke University, Durham, North Carolina.
May 1984. Second major in mathematics. 3.9/4.0 average.  Senior
Honor's thesis under the direction of Dr. Allen Biermann.}
Graduation Summa Cum Laude, May 1984;
%Phi Beta Kappa, Spring 1983.
%Liggett Group Scholarship, 1983---1984;
%Class Honors and Dean's List, 1981---1984.

\prt{Professional Service}
\bi
\item November 2001---present.  Member of the Governing Board of the
International Machine Learning Society.  (The governing board is a
group of fifteen whose principle mandate is to administer the
International Machine Learning Conference.  The members were chosen by
an open election among all attendees of the last three conferences.)
\item May 2002---present. Member of a National Research Council
Subcommittee for the review of the NASA's Computing, Information, and
Communications Technology (CICT) Program.
\item September 2001---present.  
Action Editor for {\it The Journal of Machine Learning Research\/}.
\item May 2000---September 2001. Member of the editorial 
board for the {\it Journal of Machine Learning Research.}
\item January 1997---September 2001. 
Action Editor for the journal {\it Machine Learning\/}.
\item January 1995---December 1997. Associate Editor for the 
{\it Journal of Artificial Intelligence Research}.
\item March 1998.  With Jaime Carbonell and Yiming Yang (of CMU),
editor of special issue of the journal {\it Machine Learning\/} on the
topic ``{machine learning and information retrieval\/}''.
\item January 1998---present. Member of the advisory board for
the {\it Journal of Artificial Intelligence Research}.
\item September 1997---present.  Member of the editorial 
board for {\it Applied Intelligence.}
\item Co-chair of the 1994 International Machine Learning Conference.
\item Member of advisory committees for ML-98, ML-97, ML-96, ML-95.
\item Area chair for ML-2000, SIGIR-2001, and SIGIR-2002.
\item Program committee member for KDD-2003, SIGMOD-2003, WWW-2003, 
NIPS-2002, ICML-2002, ICML-2001, SIGIR-2001, WWW-2000, 
ILP-2000, SIGIR-99, WWW-99, ILP-99,
COLT-98, ML-97, ILP-97, AAAI-96, ALT-96, ILP-95, ILP-94, AAAI-93, and
ML-93, and various specialized workshops.
\item Member of organizing committee for AAAI-92 workshop on
``Constraining Learning Using Prior Knowledge''.
\item Reviewer for numerous journals including {\it Artificial 
Intelligence}, {\it The Journal of Logic Programming}, 
{\it Information Processing Letters},
and {\it Theoretical Computer Science}.
%\item Past president of the Rutgers Computer Science Graduate Student Society.
\ei

\newpage

\prt{Teaching and Supervisory Experience}
\bi
\item Spring 2002. {\it Center for Automated Learning and Discovery,
Carnegie-Mellon University, Pittsbugh PA}. With T.~Mitchell,
taught a graduate seminar in knowledge discovery from data.
\item Fall 2000. {\it Computer Science Department,
Carnegie-Mellon University, Pittsbugh PA}. With 
J.~Baxter, A.~McCallum, T.~Mitchell, F.~Pereira, 
taught a graduate seminar in text mining and 
information extraction.
\item September 1998---April 2000.  Member of the AT\&T Labs
Fellowship Selection Committee.
\item Fall 1997. {\it Computer Science Department,
Rutgers University, New Brunswick, NJ}.  With Y.~Freund and
R.~Schapire, taught a graduate seminar in machine learning.
\item Spring 1996. {\it Computer Science
Department, Columbia University, New York, NY}.
Taught a course in machine learning.
\item Committee member for four Ph.D theses: Chunki Basu (Rutgers), 
Daniel Kudenko (Rutgers), John Zelle (University of Texas at Austin),
and Peter Whigham (Australian National University).
\ei

\prt{Invited Talks and Seminars} 
\bi
\item October 2002, invited talk, ``Exploiting Document Structure in
Information Extraction and Document Classification'', McKay
Distinguished Lecture, University of California, Berkeley.
\item October 2001, invited talk, ``Issues in Extracting Information
from the Web'', at the 7th International Workshop on Parsing
Technologies, Sponsored by ACL/SIGPARSE, Bejing, China.
\item December 2000, invited talk, ``Learning Using the Web as Background Knowledge'',
at the Eleventh International Conference on Algorithmic Learning
Theory, Sydney, Australia.
\item June 1999, keynote address, ``What can we learn from the Web?''
at the 16th International Conference on Machine Learning, Bled,
Slovenia.
\item March 1996, invited talk, ``What the Well-Informed IR
Researcher Should Know About Machine Learning'', at the 1996
AAAI Spring Symposium on Machine Learning and Information Access,
Palo Alto, CA.
\item September 1995, invited talk, 
``Learning to Classify English Text with ILP
Methods'', at the Fifth International Workshop on Inductive Logic
Programming, Leuven, Belgium.
\ei

\prt{Patents}
\bi
\item {\em Method and apparatus for extracting data from data sources on 
a network}.  Patent \#6,516,308.
\item {\em A system and method for accessing heterogeneous databases}.
Patent \#6,295,533.
\item {\em A system and method for finding information in a
distributed information system using query learning
and meta search}.  Patent \# 5,347,623.
\item {\em Rule induction on large noisy data sets}.  Patent \# 5,719,692.
\item {\em Software discovery system}.  Patent \#  5,642,472. 
\item {\em Biased learning system}.  Patents \# 5,481,650 and \# 5,627,945.
\ei

\newpage

% total pubs count = 95

\prt{Journal Publications}
\bd
\item[submitted] S.~Zelikovitz, H.~Hirsh, W.~Cohen,
	``Using and Extending WHIRL Queries for Text Classification'',
	submitted for journal publication.

\item[submitted] W.~Cohen, ``Learning and Discovering Structure in Web Pages'',
	submitted for journal publication.	

\item[in press] M.~Bilenko, R.~Mooney, W.~Cohen, P.~Ravikumar, S.~Fienberg
	``Adaptive Name-Matching in Information Integration'',
	{\it IEEE Intelligent Systems}, in press.

\item[2001] C.~Basu, H.~Hirsh, W.~Cohen, C.~Neville-Manning,
	``Technical Paper Recommendation: A Study in Combining
	  Multiple Information Source'', in {\it 
	  The Journal of Artificial Intelligence Research} 14,
	  pp 231-252.

\item[2000] W.~Cohen, 
	``Data Integration using Similarity Joins and
	a Word-based Information Representation Language'', 	
	in {\it ACM Transactions on Information Systems},
	18(3), July 2000, pp 288-321.

\item[2000] W.~Cohen and W.~Fan, ``Web-collaborative filtering: recommending
music by crawling the Web'', in {\it Computer Networks}, 33, pp 685--698.
	A version of this paper also appeared in the proceedings of
	the {\em Ninth International World Wide Web Conference
	(WWW-2000)}.

\item[2000] W.~Cohen, 
	``WHIRL: A Word-Based Information Representation Language'', 	
	{\it Artificial Intelligence}, 118, pp 163--196.

\item[2000] W.~Cohen, P.~Devanbu,
	``Automatically Exploring
	Hypotheses about Fault Prediction: a Comparative Study of Inductive
	Logic Programming Methods'',
	{\it International Journal of
	Software Engineering and Knowledge Engineering},
	9(5), pp 519--546.

\item[1999] W.~Cohen, Y.~Singer,
	``Context-sensitive learning methods for text categorization'',
	in {\it ACM Transactions on Information Systems}, 17(2), Apr 1999,
	pages 171-173.

\item[1999] W.~Cohen, Y.~Singer, R.~Schapire,
	``Learning to Order Things'', 	in
	{\it Journal of Artificial Intelligence Research},
	10, 1999, pp 243-270. 

\item[1999] W.~Cohen, W.~Fan,
	``Learning page-independent heuristics for extracting data
	from Web pages'', {\it International Journal of Computer and
	Telecommunications Networking}, 31, pp 1641--1652. Versions of
	this paper also appeared in the proceedings of 
	the {\em Eighth International World Wide Web Conference
	(WWW-99)} and {\em the 1999 AAAI Spring Symposium Workshop on Intelligent
	Agents in Cyberspace}.

\item[1999] W.~Cohen,
	``Reasoning about Textual Similarity in Information Access'',
	{\it Autonomous Agents and Multi-Agent Systems}, 2, 1999,
	pp 65--86.

\item[1998] W.~Cohen, ``The WHIRL Approach to Information Integration'', 
		{\it IEEE Intelligent Systems}, Sept/Oct 1998, pp 20--23.
		(In the {\em Trends and Controversies\/} feature
		 on information integration.)

\item[1998] W.~Cohen, ``Hardness Results for Learning 
		First-Order Representations and Programming by 
		Demonstration'', {\it Machine Learning}, 30(1),
	        pp 57--88.

\item[1996] W.~Cohen, ``Adaptive Mapping and Navigation by
		Teams of Simple Robots'', {\it Robotics
		and Autonomous Systems}, 18, pp 411--434.

\item[1996] W.~Cohen, ``Pac-Learning Non-Recursive Prolog
		Clauses'', {\it Artificial Intelligence},
		79(1), pp 1--38.

\item[1995] W.~Cohen and D.~Page, ``Polynomial Learnability 
		and Inductive Logic Programming: Methods and Results'', 
		{\it New Generation Computing}, 13(3).

\item[1995] W.~Cohen, ``Pac-Learning Recursive Logic
		Programs: Efficient Algorithms'', {\it
		Journal of Artificial Intelligence Research},
		Vol 2, pp 500--539.

\item[1995] W.~Cohen, ``Pac-Learning Recursive Logic
		Programs: Negative Results'', {\it
		Journal of Artificial Intelligence Research}.
		Vol 2, pp 541--573.

\item[1995] W.~Cohen, ``Inductive Specification Recovery: 
		Understanding Software by Learning from Example Behaviors'',
		{\it Automated Software Engineering},
		2(2).

\item[1994] W.~Cohen, H.~Hirsh, ``Learnability of Description Logics
		with Equality Constraints'', 
		{\em Machine Learning\/}, 17(2/3).

\item[1994] 	W.~Cohen, ``Grammatically Biased Learning:
		Learning Logic Programs Using an Explicit 
		Antecedent Description Language'', 
		{\em Artificial Intelligence}, Vol 68, pp 303-366.

\item[1994] 	W.~Cohen, ``Incremental Abductive EBL'', 
		{\em Machine Learning\/}, 15(1).  

\item[1994]     L.~T.~McCarty, W.~Cohen, ``The Case for Explicit
		Exceptions'', in {\em Methods of
		Logic in Computer Science}, 1(1).

\item[1992] 	W.~Cohen, ``Abductive Explanation-Based Learning:
		A Solution to the Multiple Inconsistent Explanation
		Problem in Explanation-Based Learning'', 
		{\em Machine Learning}, 8(2).

\item[1992] 	W.~Cohen, ``Using Distribution-Free Learning Theory
		to Analyze Solution Path Caching Mechanisms'',
		{\em Computational Intelligence}, 8(2).

\item[1986]	K.~Bartlett, W.~Cohen, A.~De Geus, G.~Hachtel,
		``Synthesis and Optimization of Multi-level Logic
		Under Timing Constraints'', {\em IEEE Transactions on
		Computer-Aided Design}, October 1985. 

\item[1985]	A.~De Geus, W.~Cohen, ``Optimization of
		Combinational Logic Using a Rule-Based Expert
		System'', {\em IEEE Design and Test of Computers},
		August 1985.
\ed

\prt{Book Chapters}
\bd
\item[2003] W.~Cohen, M.~Hurst, L.~S.~Jensen, 
	``A Flexible Learning System for Wrapping Tables and Lists in HTML Documents'', 
	in ``Web Document Analysis: Challenges and Opportunities'', ed. Antonacopoulos \& Hu, 
	Word Scientific Publishing.

\item[1996] W.~Cohen, ``Learning to Classify English Text with 
	ILP Methods'', in ``Advances in ILP'',
	ed.~L.~de Readt, IOS Press. 

\item[1994] W.~Cohen, R.~Greiner, D.~Schuurmans,
	``Probabilistic Hill-Climbing'',
	in ``Computational learning theory and
	natural learning systems (Volume II)'', MIT Press.

\item[1994] H.~Hirsh, W.~Cohen, ``Learning from Data with Bounded 
	Inconsistency: Theoretical and Experimental Results'', 
	in ``Computational learning theory and natural learning
	systems (Volume I)'', MIT Press.

%W.~Cohen, R.~Greiner and D.~Schuurmans,
%``Probabilistic Hill-Climbing'',
%in {\em Computational Learning Theory and Natural Learning Systems,
%Volume II: Intersection between Theory and Experiment},
%ed.~S.~Hanson, T.~Petsche, M.~Kearns and R.~Rivest,
%Chapter 11, p.~171--81, MIT Press, 1994.

\ed

\prt{Rigorously Refereed Conference Publications}
\bd
\item[2003] C.~Zhai, W.~Cohen, J.~Lafferty,
	``Beyond Independent Topical Relevance: Methods and Evaluation Metrics for Subtopic Retrieval'',
	in {\it Proceedings of the 26th Annual International ACM SIGIR Conference (SIGIR-2003)}.

\item[2003] W.~Cohen, R.~Wang, R.~F.~Murphey,
	``Understanding Captions in Biomedical Publications''
	in {\em Proceedings of the Ninth International Conference on Knowledge Discovery and
	Data Mining (KDD-2003)}.

\item[2003] W.~Cohen,
	``Infrastructure Components for Large-Scale Information Extraction
	Systems'', in {\em Proceedings of the 
	Fifteenth Innovative Applications of Artificial 
	Intelligence Conference (IAAI-03)}.

\item[2002] W.~Cohen,
	``Improving A Page Classifier with Anchor Extraction and Link
	Analysis'', in {\em Neural Information Processing
	(NIPS-2002)}.

\item[2002] W.~Cohen, J. Richman, 
	``Learning to Match and Cluster Large High-Dimensional Data
	Sets For Data Integration'', in {\em Proceedings of
	the Eighth International Conference on Knowledge Discovery and
	Data Mining (KDD-2002)}.

\item[2002] W.~Cohen,  M.~Hurst and L.~Jensen, 
	``A Flexible Learning System for Wrapping Tables and Lists in
	HTML Documents'', in {\em Proceedings of the Eleventh
	International World Wide Conference (WWW-2002)}.

\item[2000] W.~Cohen, ``Automatically extracting features for concept learning from the Web'',
	in {\em Proceedings of the Seventeenth International Machine Learning
	Conference} (ICML-2000). 

\item[2000] W.~Cohen, H.~Kautz, D.~McAllester ``Hardening Soft 
	Information Sources'' in {\em Proceedings of the Sixth
	International Conference on Knowledge Discovery and Data Mining}
	(KDD-2000).

\item[1999] W.~Cohen and Y.~Singer, ``A Simple, Fast, and Effective
	Rule Learner'', in {\em Proceedings, 
	Seventeenth National Conference on
	Artificial Intelligence} (AAAI-99).

\item[1999] W.~Cohen, ``Recognizing Structure in Web Pages using Similarity Queries'', 
	in {\em Proceedings, Seventeenth National Conference on
	Artificial Intelligence} (AAAI-99).

\item[1998] W.~Cohen, ``Joins that Generalize: Text Classification
	Using a Similarity-Based Database'', in {\em Proceedings of the Fourth
	International Conference on Knowledge Discovery and Data Mining}
	(KDD-98).

\item[1998] C.~Basu and H.~Hirsh and W.~Cohen, ``Recommendation as
		Classification: Combining Social and Content-Based Information in
		Recommendation'', in 
		{\em Proceedings, 
		Sixteenth National Conference on
		Artificial Intelligence} (AAAI-98).

\item[1998] W.~Cohen, ``Integration of Heterogeneous Databases Without
		Common Domains Using Queries Based on Textual Similarity'',
		in {\em Proceedings of ACM SIGMOD International Conference
		on Management of Data} (SIGMOD-98).

\item[1998] W.~Cohen, ``A Web-based Information System that Reasons
		with Structured Collections of Text'', in 
		{\em Autonomous Agents 1998.}

\item[1997] W.~Cohen and R.~Schapire and Y.~Singer, ``Learning to
		Order Things'' in {\em Proceedings of the 
		1997 Conference on Neural
		Information Processing Systems} (NIPS-97).

\item[1997] W.~Cohen and D.~Kudenko, ``Transferring and Retraining 
		Learned Information Filters'', in {\em Proceedings, 
		Fifteenth National Conference on
		Artificial Intelligence} (AAAI-97).

\item[1997] W.~Cohen and P.~Devanbu, ``A Comparative Study of 
		Inductive Logic Programming Methods for Software 
		Fault Prediction'', {\em  Machine Learning, Proceedings
		of the Fourteenth International Conference} (ML-96).

\item[1996] W.~Cohen and Y.~Singer, ``Context-sensitive Learning Methods for 
		Text Categorization'', 
		in {\em Nineteenth Annual International ACM SIGIR
		Conference on Research and Development in 
		Information Retrieval} (SIGIR-96). 

\item[1996] W.~Cohen, ``Learning Trees and Rules with Set-Valued Attributes'', 
		in {\em Proceedings, Fourteenth National Conference on
		Artificial Intelligence} (AAAI-96).

\item[1996] W.~Cohen, ``The Dual DFA Learning Problem:
		Hardness Results for Programming by Demonstration
		and Learning First-Order Representations'',
		in {\em Proceedings of the Ninth Annual
		ACM Conference on Computational Learning
		Theory} (COLT-96).

\item[1995] W.~Cohen, ``Fast Effective Rule Induction'', 
		in {\em  Machine Learning, Proceedings
		of the Twelfth International Conference} (ML-95).

\item[1995] W.~Cohen, ``Text Categorization and Relational Learning'', 
		in {\em  Machine Learning, Proceedings
		of the Twelfth International Conference} (ML-95).

\item[1994] W.~Cohen, ``Pac-learning Nondeterminate Clauses'', 
		in {\em Proceedings, Twelth National Conference on
		Artificial Intelligence} (AAAI-94).

\item[1994] W.~Cohen, ``Recovering Software Specifications with 
		Inductive Logic Programming'',
		in {\em Proceedings, Twelth National Conference on
		Artificial Intelligence} (AAAI-94).

\item[1994] W.~Cohen and H.~Hirsh, ``Learning the CLASSIC Description 
		Logic: Theoretical and Experimental Results'', 
		in {\em Principles of Knowledge Representation and
		Reasoning: Proceedings of the Fourth International
		Conference\/}  (KR-94).

\item[1993] W.~Cohen, ``Cryptographic Limitations
		on Learning One-Clause Logic Programs'', 
		in {\em Proceedings of the Eleventh National Conference
		on Artificial Intelligence} (AAAI-93).

		This paper was also one of ten papers 
		nominated for the Best Written Paper Award.

\item[1993] W.~Cohen, ``Pac-Learning a Restricted Class of
		Recursive Logic Programs'', 
		in {\em Proceedings of the Eleventh National Conference
		on Artificial Intelligence} (AAAI-93).   

\item[1993] W.~Cohen, ``Efficient Pruning Methods for
		 Separate-and-Conquer Rule Learning Systems'',
		in {\em Proceedings of the 13th International
		Joint Conference on Artificial Intelligence} (IJCAI-93).

\item[1992] 	W.~Cohen, A.~Borgida, H.~Hirsh ``Computing Least
		Common Subsumers in  Description Logics'', in {\em
		Proceedings of the Tenth National Conference on
		Artificial Intelligence} (AAAI-92).  

\item[1992] 	W.~Cohen, ``Compiling Prior Knowledge Into An Explicit
		Bias'', in {\em Proceedings of the Eighth Annual
		Conference on Machine Learning} (ML-92). 

\item[1992] 	W.~Cohen, H.~Hirsh, ``Learnability of Description Logics'',
		in {\em Proceedings of the Fourth Annual Workshop
		on Computational Learning Theory} (COLT-92).

\item[1990]	W.~Cohen, ``Using Distribution-Free Learning Theory to
		Analyze Chunking'', in {\em Proceedings of the
		Canadian Conference on Artificial Intelligence}.

\item[1990]	W.~Cohen, ``Learning Approximate Control Rules of High
		Utility'', in {\em Proceedings of the Seventh
		International Machine Learning Conference} (ML-90). 

\item[1990]	W.~Cohen, ``An Analysis of Representation Shift in
		Concept Learning'', in {\em Proceedings of the Seventh
		International Machine Learning Conference} (ML-90).

\item[1990]	W.~Cohen, ``Learning from Textbook Knowledge: A Case Study'',
		in {\em Proceedings of the Eighth National Conference
		on Artificial Intelligence} (AAAI-90).

\item[1988]	W.~Cohen, ``Generalization of Number and Learning from
		Multiple Examples in Explanation Based Learning'',
		in {\em Proceedings of the Fifth International Machine
		Learning Conference} (ML-88).

\ed


\prt{Other Conference and Workshop Publications}
\bd
\item[2003] W.~Cohen, Z.~Kou R.~Murphy,
	``Extracting Information from Text and Images for Location Proteomics'',
	in {\it Proceedings of the 3rd Workshop on Data Mining in Bioinformatics,
	held in conjunction with 9th ACM SIGKDD International Conference on Knowledge Discovery and Data Mining
		(KDD'2003)}

\item[2003]W~.Cohen, P.~Ravikumar, S.~Fienberg,
	``A Comparison of String Metrics for Matching Names and Records'',
	in {\it Proceedings of the Workshop on Data Cleaning and Object Consolidation,
	held in conjunction with 9th ACM SIGKDD International Conference on Knowledge Discovery and Data Mining
		(KDD'2003)}.

\item[2003]W~.Cohen, P.~Ravikumar, S.~Fienberg,
	``A Comparison of String Distance Metrics for Name-Matching
	Tasks'', in {\it Proceedings of the 2003 Workshop on
	Information Integration on the Web (IIWeb-03), held in
	conjunction with the Eighteenth International Joint Conference
	On Artificial Intelligence (IJCAI-03).}

\item[2001] W.~Cohen and J.~Richman, ``Learning to Match and Cluster Entity 
Names'', in {\em Proceedings of the ACM SIGIR-2001 Workshop on Mathematical/Formal Methods in
Information Retrieval}.

\item[2001] W.~Cohen and L.~Jensen, ``A Structured Wrapper Induction 
System for Extracting Information from Semi-Structured Documents'', in
{\em Proceedings of the IJCAI-2001 Workshop on Adaptive Text
Extraction and Mining}.

\item[2001] L. Jensen and W.~Cohen, ``Grouping Extracted Fields'',
in {\em Proceedings of the IJCAI-2001 Workshop on Adaptive Text
Extraction and Mining}.

\item[2000] W.~Cohen, ``Learning Using the Web as Background Knowledge'',
	abstract of invited talk at the {\em Eleventh International
	Conference on Algorithmic Learning Theory}, Sydney, Australia.

\item[1999] W.~Cohen, ``What Can We Learn from the Web?'', abstract of
	the keynote address at the {\em Sixteenth International Machine Learning
	Conference}, Bled, Slovenia.

\item[1999] W.~Cohen, ``Some practical observations on integration of
	Web information'', in {\em the ACM Sigmod Workshop on the Web 
	and Databases (WebDB'99)}. 

\item[1998] W.~Cohen, ``The WHIRL Approach to Integration: An Overview'',
		in the {\em AAAI-98 Workshop on AI and Information 
		Integration}.  

		This paper was the only submission to be
		selected for full plenary presenation.

\item[1997] W.~Cohen, ``Knowledge Integration for Structured
		Information Sources Containing Text (Extended
		Abstract)'', in the {\em SIGIR-97 Workshop on
		Networked Information Retrieval}.

\item[1996] W.~Cohen and Y.~Singer, ``Learning to Query the Web'',
	    	in {\em Proceedings of the 1996 AAAI Workshop
		on Internet-based Information Systems}.

\item[1996] W.~Cohen, ``Learning Rules that Classify E-mail'',
	    	in {\em Proceedings of the AAAI Spring Symposium on 
		Machine Learning and Information Access}.

\item[1993] 	W.~Cohen, ``A Review of `Creating a Memory of
		Causal Relationships' by Michael Pazzani'', 
		{\em Machine Learning}.

\item[1993] P.~Rosenbloom, H.~Hirsh, W.~Cohen, B.~Smith, ``Two 
	    	frameworks for integrating knowledge in induction'',
		in {\em Proceedings of the Seventh Annual Workshop on 
		Space Operations, Applications,	and Research (SOAR '93)}

\item[1993] W.~Cohen, ``Rapid Prototyping of ILP Systems Using Explicit 
		Bias'' in {\em Proceedings of the 1993
		IJCAI Workshop on Inductive Logic Programming}.

\item[1993] W.~Cohen, ``Learnability of Restricted Logic Programs'',
		in {\em Proceedings of the Third International
		Workshop on Inductive Logic Programming} (ILP-93).

\item[1992] 	W.~Cohen, ``Desiderata for Generalization-to-N Algorithms'', 
		in {\em Analogical and Inductive Inference: Proceedings
		of International Workshop} (AII-92).

\item[1991]	W.~Cohen ``The Generality of Overgenerality'',
		in {\em Proceedings of the Eighth International 
		Machine Learning Workshop} (ML-91).

\item[1991] 	R.~Greiner, W.~Cohen ``Probabilistic Hill-Climbing'',
		in {\em Proceedings of the 1991 Workshop on Computational
		Learning Theory and Natural Learning Systems} (CLNL-91).

\item[1990]	W.~Cohen, ``Learning from Examples and an `Abductive
		Theory'$\,$'', in {\em Proceedings of the 1990
		AAAI Spring Symposium on Abduction}.

\item[1988]	W.~Cohen, J.~Mostow, A.~Borgida, ``Generalizing Number
		in Explanation Based Learning'', {\em Proceedings of
		the 1988 AAAI Spring Symposium on Explanation-Based 
		Learning}.

\item[1987]	T.~Hornick, W.~Cohen, G.~Miller, ``A Natural Language
		Query System for Hubble Space Telescope Proposal
		Selection'', in {\em Proceedings of the Goddard
		Conference on Space Applications of Artificial
		Intelligence and Robotics}.

\item[1987]	G.~Miller, D.~Rosenthal, W.~Cohen, M.~Johnston,
		``Expert Systems Tools for Hubble Space Telescope
		Scheduling'', in {\em Proceedings of the Goddard
		Conference on Space Applications of Artificial
		Intelligence and Robotics.}

\item[1985]	K.~Bartlett, W.~Cohen, A.~De Geus, G.~Hachtel,
		``Synthesis and Optimization of Multi-level Logic
		Under Timing Constraints'', in {\em Proceedings of the
		IEEE International Conference on Computer-Aided
		Design}.

\item[1985]	W.~Cohen, K.~Bartlett, A.~De Geus, ``Impact of
		Metarules in a Rule-Based Expert System for Gate Level
		Optimization'', in {\em Proceedings of the IEEE
		International Symposium on Circuits and Systems}.


\item[1984]	K.~Garrison, D.~Gregory, W.~Cohen, A.~De Geus,
		``Automatic Area and Performance Optimization of
		Combinatorial Logic'', in {\em Proceedings of the IEEE
		International Conference on Computer-Aided Design}.
\ed

\iffalse
\newpage

\section*{References for William W. Cohen}

\bi
\item Thomas G. Dietterich (tgd@cs.orst.edu), 
Professor, Computer Science Department, 
Oregon State University, Corvallis, Oregon.

\item Tom Mitchell (tom.mitchell@cs.cmu.edu),
Fredkin Professor of AI and Learning and 
Director, Center for Automated Learning and Discovery, 
School of Computer Science, 
Carnegie Mellon University,
Pittsbugh, PA.

\item Ray Mooney (mooney@cs.utexas.edu),
Professor, Department of Computer Sciences, 
The University of Texas at Austin, 
Austin, Texas.

\item Fernando Pereira (pereira@cis.upenn.edu)
Andrew and Debra Rachleff Professor and
Chair, Department of Computer and Information Science,
University of Pennsylvania,
Philadelphia, PA.

\item J. Ross Quinlan (quinlan@cse.unsw.edu.au),
Adjunct Professor, School of Computer Science and Engineering,
University of New South Wales,
Sydney, Australia.

\ei
\fi

\end{document}
